cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-17 paper-cardinalR.Rmd
Added alt-txt for cone data projections

```{r cone-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from the $3\\text{-}D$ \\texttt{cone} data. Points are concentrated near the tip along the height dimension, while the radius of the hyperspherical cross-section decreases linearly toward the apex. These projections show how the conical geometry is preserved.", fig.pos="H", fig.alt="Three $2\\text{-}D$ projections of the 3-D cone dataset, showing points concentrated near the tip and the linear decrease in radius toward the apex.", fig.pos="!ht", fig.width=12, fig.height=4}

>>>>

```{r cone-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from the $3\\text{-}D$ \\texttt{cone} data. Points are concentrated near the tip along the height dimension, while the radius of the hyperspherical cross-section decreases linearly toward the apex. These projections show how the conical geometry is preserved.", fig.pos="H", fig.alt=" A 2D scatterplot shows the projection of a high-dimensional cone-shaped point cloud. The horizontal and vertical axes are unlabeled numeric coordinates, each spanning a roughly symmetric range around zero (for example, from about -1 to 1). Hundreds of points form a dense cluster near one end of the plot, corresponding to the cone’s apex, with density gradually decreasing as points extend outward in a flared, cone-like or triangular region. There are no colours, shapes, or facets used; all points share the same appearance, and the key visible pattern is the concentrated tip transitioning smoothly into a wider spread of points, illustrating a cone structure in projection.", fig.pos="!ht", fig.width=12, fig.height=4}

### 2025-12-17 paper-cardinalR.tex
Updated Table 1
Added alt-txt for cone data projections

\caption{\label{tab:main-tb-pdf}The main arguments for \texttt{gen\_multicluster()}.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Argument & Type & Explanation\\
\midrule
\texttt{n} & numeric (vector) & Number of points in each cluster.\\
\texttt{k} & numeric & Number of clusters.\\
\texttt{loc} & numeric (matrix) & Locations/centroids of clusters.\\
\texttt{scale} & numeric (vector) & Scaling factors of clusters.\\
\texttt{shape} & character (vector) & Shapes of clusters.\\
\texttt{rotation} & numeric (list) & Rotation matrices, one per cluster.\\
\texttt{is\_bkg} & boolean & Background noise should exist or not.\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
\includegraphics[width=1\linewidth,alt={Three $2\text{-}D$ projections of the 3-D cone dataset, showing points concentrated near the tip and the linear decrease in radius toward the apex.}]{paper-cardinalR_files/figure-latex/cone-proj-1} \caption{Three $2\text{-}D$ projections from the $3\text{-}D$ \texttt{cone} data. Points are concentrated near the tip along the height dimension, while the radius of the hyperspherical cross-section decreases linearly toward the apex. These projections show how the conical geometry is preserved.}\label{fig:cone-proj}
\end{figure}

>>>>

\caption{\label{tab:main-tb-pdf}The main arguments for \texttt{gen\_multicluster()}.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Argument & Type & Explanation\\
\midrule
\texttt{n} & integer (vector) & Number of points in each cluster.\\
\texttt{k} & integer & Number of clusters.\\
\texttt{loc} & numeric (matrix) & Locations/centroids of clusters.\\
\texttt{scale} & numeric (vector) & Scaling factors of clusters.\\
\texttt{shape} & character (vector) & Shapes of clusters.\\
\texttt{rotation} & numeric (list) & Rotation matrices, one per cluster.\\
\texttt{is\_bkg} & boolean & Background noise should exist or not.\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[!ht]
\includegraphics[width=1\linewidth,alt={ A 2D scatterplot shows the projection of a high-dimensional cone-shaped point cloud. The horizontal and vertical axes are unlabeled numeric coordinates, each spanning a roughly symmetric range around zero (for example, from about -1 to 1). Hundreds of points form a dense cluster near one end of the plot, corresponding to the cone’s apex, with density gradually decreasing as points extend outward in a flared, cone-like or triangular region. There are no colours, shapes, or facets used; all points share the same appearance, and the key visible pattern is the concentrated tip transitioning smoothly into a wider spread of points, illustrating a cone structure in projection.}]{paper-cardinalR_files/figure-latex/cone-proj-1} \caption{Three $2\text{-}D$ projections from the $3\text{-}D$ \texttt{cone} data. Points are concentrated near the tip along the height dimension, while the radius of the hyperspherical cross-section decreases linearly toward the apex. These projections show how the conical geometry is preserved.}\label{fig:cone-proj}
\end{figure}
